State of the Art Review on Privacy-Preserving Signatures, Credentials, and Authentication

### 2021-11-26 prism-backend/research/soa_review/ac.tex
Polished version. Still early draft, but at least readable (excluding DAA section, which is not a priority for now).

\paragraph{Main intuition.}
%
Anonymous Credentials (ACs) were first proposed by Chaum \cite{chau85}, and
further studied, formally treated, and optimized, in a series of papers by
Camenisch and Lysyanskaya \cite{cl01,cl02,cl04} and, independently, by Brands
\needcite\footnote{Camenisch and Lysyanskaya line of work is well known for
  IBM's Idemix system, and Brands's work for Microsoft's U-Prove. More detail
  appears in the sequel.}. In an AC system, roughly speaking, users receive
credentials from an issuing organization, which they can then use to
authenticate against some verifier. The main property is that this
authentication process can be done in a privacy-preserving way. This typically
means that the verifier cannot link different authentication processes by that
same user. Usually, credentials are composed by multiple attributes, such that
the verifier only learns the attributes that the user is willing to share (or a
function of them).

@@

Usually, the commitment to the user's secret key is known as a pseudonym, or
in short form, \emph{nym}. These nyms have proven to be a useful component to
ensure security and privacy properties -- and are also leveraged in many group
signature and DAA works.

A large part of the academic works in the AC domain follow this approach, which
is then extended to support enhanced functionality. For instance, in order to
support multiple issuers (and, in some sense, multiple attributes)
\cite{cl01,cl02,cl04} \todo{check if the references are correct} require an
extra protocol for proving, in zero-knowledge, equality of two committed and signed values.
This allows user $A$, with credential $\sigma_A^I$ obtained from issuer $I$ and
credential $\sigma_A^J$ obtained from issuer $J$, to prove $J$ that she has a
valid credential from $I$, by issuing a zero-knowledge proof of equality for
both credentials. Now, if each credential is associated with a different set of
attributes, this also lets to ``naively'' build multi-attribute AC systems.

For multi-attribute ACs, though, much more efficient variants are possible. To
begin with, CL signatures allow signing blocks of messages (and commitments),
which can be seen as attributes signed by the issuer. BBS+ signatures
\cite{am06,cdl16b}, and PS16 signatures \cite{ps16} also support similar
functionality, and have been leveraged to build multi-attribute AC systems
too (e.g., \cite{cks10} gives a construction with BBS+ credentials, and
\cite{sms+19,halp20} are based on PS16). These family of signatures on blocks
of messages have yet another very useful property: signatures are easily
randomizable, which can be used (along with the previously mentioned
zero-knowledge proofs) to make unlinkable showings of the same credential.
AC systems achieving the latter property of unlinkable showings are said
to offer \emph{multi-show} credentials.

@@

Restricting the expressiveness, and focusing on letting the credential holder
reveal only a subset of the attributes in a credential, more efficient schemes
have been proposed, leveraging algebraic tricks such as structure-preserving
signatures on equivalence classes (SPS-EQ), along with vector commitment schemes
\cite{cdhk15}, or set commitment schemes \cite{fhs19}. The former uses Lagrange
interpolation to allow revealing only a subset of the committed messages;
\todo{what was the specific technique of \cite{fhs19}?}. \cite{fhs19}, is more
efficient, as avoids complex zero-knowledge proofs; however it does not support
blind issuance of credentials, as opposed to \cite{cdhk15} \todo{confirm this
  last part, and refine}.
%
Also improving efficiency, but restricting to the scenario in which the issuer
is the same entity as the verifier (as in ticketing systems for public transport),
\cite{cmz14}, replaces signatures with algebraic MACs.

Somewhat similar is the approach to (delegatable) credentials that builds on
signatures with controlled malleability \cite{bcc+09,cklm14}, where \cite{cklm14}
is a generalization of \cite{bcc+09}. Roughly, credentials are signatures, built
from non-interactive zero-knowledge proofs of knowledge, on commitments to the
user key, that support \emph{controlled malleability}. This malleability means
that both the proof and the statements can be randomized and transformed, but
only for allowed transformatoins. The specific transformation considered for
delegation requires that a credential with depth $L$, can only produce a credential
with level $L+1$. Credential showings are also represented through transformations,
through which the holder proves knowledge, and equality, of the secret in the
``source'' and ``target'' nyms. Although the credentials in these works do not
include multiple attributes (some hint on how to support public attributes is
given in \cite{bcc+09}), it is certainly possible to do so through a proper
transformation -- although, probably, the result won't be very efficient if
done naively \todo{specific figures?} The notion of transformations is interesting,
though, as the authors prove that it is similar (or even more generic) than those
used to achieve expresiveness in related digital singature schemes (such as
policy-based signatures \needcite and delegatable functional signatures \needcite).
Thus, it is reasonable to expect that very expressive AC systems could be built
with this approach.

All AC systems mentioned up to this point follow, up to small variations, the
same approach: randomizable signatures on sets of (committed) messages, with
(somehow) efficient proofs. A completely different approach is described in
\cite{dmm+18}, based on predicate encryption. In predicate encryption, given
a master key pair, decryption keys associated with specific predicates can be
derived. Messages, and attribute sets, are encrypted with the master public key,
such that the resulting ciphertext can only be decrypted with a decryption key
associated with a predicate that is satisfied by the attributes in the
ciphertext. Assume an attribute space that can be represented by binary strings
$\Sigma$. On one hand, policies defined by verifiers in \cite{dmm+18} are encoded
as binary circuits through strings in $\Sigma$ too\footnote{\todo{This seems
    like an abuse of predicate encryption, as encryption receives a predicate,
    rather than an attribute set.}}, which can thus be associated to
ciphertexts through the predicate encryption process. On the other hand,
credentials received by users are decryption keys on a generic policy $f$, with
a hardcoded set of attributes (the attributes that the user is granted), that
can evaluate circuits. Then, intuitively, in order for a verifier to check
whether a user owns a attribute-based credential meeting certain policy $g$, it
creates a ciphertext with encoding a circuit for $g$. If the user can decrypt
this ciphertext, the verifier accepts. This only supports public attributes
(i.e., known to the issuer), though. A negative part of this approach is that
credential showings can only be interactive, whereas in the randomizable proofs
approach, they can be made non-interactive too.

\subsubsection{Main Security Models.}
%
All AC systems include \emph{anonymity} and \emph{unforgeability} as main
security properties. Up to minor variations depending on extra functionality,
anonymity typically captures that, concerning a user's credential, nothing
should be learnt by third parties that the user does not explicitly reveal.
E.g., for ACs that support multiple attributes and selectively disclosing
subsets of them, anonymity captures that the information leaked during a showing
of such credential is limited to the subset of attributes voluntarily revealed
by the user. Since multi-show credentials are also the most common type,
anonymity also captures that two different showings must be unlinkable.
As mentioned, further variations in the functionality affect anonymity --
e.g., in systems supporting delegation, the delegation chain may be required
to be kept private.
% 
Concerning unforgeability, it basically captures that no adversary can make
a verifier accept a credential that has not been honestly produced by an
issuer of the system. Again, there are variations to this. For instance, when
credentials are composed of attributes that can further be selectively
disclosed. In this case, the adversary should not be able to prove ownership
of a set of attributes not contained within the set of attributes that have
been leaked.a showing that include attributes not contained in credentials leaked to the
adversary.

Special mention is worth to the model variation in \cite{hs20}, which divides
the user into two entities: core and helper, thus taking anonymous credentials
closer to DAA. This is reflected into the model by adding a property named
\emph{dependability}, which requires that no adversary should be capable to
show an honestly generated credential withouth compromising the core entity.

On the approach to formalize AC security notions, game-based definitions tend
to be more frequent \needcite, also including definitions in the simulation
paradigm. The UC framework has also been used \needcite, even in combination
with game-based definitions \needcite.

\subsubsection{Variations in functionality.}
%
Multi-attribute and multi-show credentials, with selective disclosure, are
the most frequent \needcite.  Blind issuance, i.e., letting users include in
their credentials attributes that are kept hidden from issuers, is also frequent
(and certainly useful to, e.g., include secret keys) \needcite. Delegation has
gained attention in the last decade \needcite, as well as supporting more
expressive proofs. While the latter is indeed possible in the early works
(one can use general zero-knowledge proofs on discrete logarithms given a
CL-, BBS- or PS16- based credential) it is worth noting that the costs are
probably too high, and it also needs to be considered in the model.
%
Perhaps surprisingly, revocation is not a common functionality, although it is
certainly considered by several works \needcite.
%
Threshold issuance is also interesting for decentralized scenarios, but it
was only considered in \cite{sms+19} and, consequently, in \cite{halp20}
(which builds on \cite{sms+19}).
%
And, finally, an interesting variation that only one work seems to target,
is that of efficient aggregation of credentials created by different issuers
\cite{cl11}. As in the topic of expressiveness, this is easily doable with the
conventional approaches: e.g., if the owner of credential A and credential B
wants to use both credentials in the same showing, she just has to prove that
they share the same secret key (although this is only possible in schemes that
embed a user secret within the credential). Still, even if possible and even
supported, this process is inefficient. \cite{cl11} leverages aggregatable
signatures, which target precisely that setting.

@@

\subsubsection{Main challenges.}
%

\subsection{Related Primitives}
\label{ssec:acrelated}

@@

\subsection{TODOs}

\begin{itemize}
\item \cite{bckl08}.
\item \cite{sand20}.
\item \cite{kkl+16}: achieves similar results to \cite{cgm16} with a different approach?
\end{itemize}

[ToPS paper I reviewed] refers to a strategy to do threshold issuing in \cite{bbh06}.

Concepts in ACs: multishow, one-show (Brands et al); interactive vs non-interactive
showings (differentiation made in \cite[p.6]{fhs19} but, why would one want interactive,
in the real world?)

Which schemes support comibning credentials from multiple issuers? I think this
is directly obtained in the schemes following the CL approach; but others?

A recurrent claim in schemes avoiding using zero-knowledge proofs of knowledge
of some attributes being included in a credential is that these proofs are costly
(like, linear in the number of attributes). Yet, they resort to other primitives
that may also be costly (e.g., predicate encryption \cite{dmm+18}) or somehow move
the cost to some other place (e.g., \cite{fhs19} uses a vector commitment scheme
that requires a public key with size that grows with the number of attributes
that \emph{can} be committed). It would be nice to have a detailed and complete
(e.g., not skipping the data that makes one scheme look bad, like the size of
the public keys) comparison. And, ideally, with concrete instantiations (not only
theoretical analysis)?

\cite{fhs19} has a nice comparison table.

>>>>

\paragraph{Main intuition.}
%
Anonymous Credentials (ACs) were first proposed by Chaum \cite{chau85}, and
further studied, formally treated, and optimized, in a series of papers by
Camenisch and Lysyanskaya \cite{cl01,cl02,cl04} and, independently, by Brands
\cite{bran00}\footnote{Camenisch and Lysyanskaya line of work is well known for
  IBM's Idemix system, and Brands's work for Microsoft's U-Prove. More detail
  appears in the sequel.}. In an AC system, roughly speaking, users receive
credentials from an issuing organization, which they can then use to
authenticate against some verifier. The main property is that this
authentication process can be done in a privacy-preserving way. This typically
means that the verifier cannot link different authentication processes by that
same user. Also, usually, credentials are composed by multiple attributes, such
that the verifier only learns the attributes that the user is willing to share
(or a function of them).

@@

Usually, the commitment to the user's secret key is known as a pseudonym, or
in short form, \emph{nym}. These nyms have proven to be a useful component to
ensure security and privacy properties -- and are also leveraged in many group
signature and DAA works. Not all anonymous credentials systems use pseudonyms,
though.

A large part of the academic works in the AC domain follow this approach, which
is then extended to support enhanced functionality. For instance, in order to
let a user with two different credentials prove being the owner of both of
them, \cite{cl01,cl02,cl04} require an extra protocol for proving, in
zero-knowledge, equality of two committed and signed values.
This allows user $A$, with credential $\sigma_A^I$ obtained from issuer $I$ and
credential $\sigma_A^J$ obtained from issuer $J$, to prove $J$ that she has a
valid credential from $I$, by issuing a zero-knowledge proof of equality for
both credentials. Furthermore, if each credential is associated with a different
(set of) attribute(s), this also leads to ``naive'' constructions of
multi-attribute AC systems.

For multi-attribute ACs, though, much more efficient variants are possible. To
begin with, CL signatures allow signing blocks of messages (and commitments),
which can be seen as attributes signed by the issuer. BBS+ signatures
\cite{asm06,cdl16b}, and PS16 signatures \cite{ps16} also support similar
functionality, and have been leveraged to build multi-attribute AC systems
too (e.g., \cite{cks10} gives a construction with BBS+ credentials, and
\cite{sms+19,halp20} are based on PS16). These family of signatures on blocks
of messages have yet another very useful property: signatures are easily
randomizable, which can be used (along with the previously mentioned
zero-knowledge proofs) to make unlinkable showings of the same credential.
AC systems achieving the latter property of unlinkable showings are said
to offer \emph{multi-show} credentials.

@@

Restricting the expressiveness, and focusing on letting the credential holder
reveal only a subset of the attributes in a credential, more efficient schemes
have been proposed, leveraging algebraic tricks such as structure-preserving
signatures on equivalence classes (SPS-EQ), along with vector commitment schemes
\cite{cdhk15}, or set commitment schemes \cite{fhs19}. The former uses Lagrange
interpolation to allow revealing only a subset of the committed messages;
while \cite{fhs19} employs set commitment schemes, mapping the attributes to
be committed to roots of a polynomial, so that opening a specific subset of the
commmitted elements just requires revealing a subset of the roots of the
polynomial.
%
Also improving efficiency, but restricting to the scenario in which the issuer
is the same entity as the verifier (as in ticketing systems for public transport),
\cite{cmz14}, replaces signatures with algebraic MACs.

Within this line of credentials from randomizable signatures, we can also find
systems that can achieve high expressiveness, like the (delegatable) credentials
building on signatures with controlled malleability \cite{bcc+09,cklm14},
where \cite{cklm14} is a generalization of \cite{bcc+09}. Here, at a high level,
credentials are signatures, built from non-interactive zero-knowledge proofs of
knowledge, on commitments to the user key, that support \emph{controlled
  malleability}. This malleability means
that both the proof and the statements can be randomized and transformed, but
only for allowed transformatoins. The specific transformation considered for
delegation requires that a credential with depth $L$, can only produce a credential
with level $L+1$. Credential showings are also represented through transformations,
through which the holder proves knowledge, and equality, of the secret in the
``source'' and ``target'' nyms. Although the credentials in these works do not
include multiple attributes (some hint on how to support public attributes is
given in \cite{bcc+09}), it is certainly possible to do so through a proper
transformation -- although, probably, the result won't be very efficient if
done naively \todo{specific figures?} The notion of transformations is interesting,
though, as the authors prove that it is similar (or even more generic) than those
used to achieve expressiveness in related digital singature schemes (such as
policy-based signatures \cite{bf14} and delegatable functional signatures \cite{bms16}).
Thus, it is reasonable to expect that very expressive AC systems could be built
with this approach.

All AC systems mentioned up to this point follow, up to ``small'' variations,
the same approach: randomizable signatures on sets of (committed) messages, with
(somehow) efficient proofs. A completely different approach is described in
\cite{dmm+18}, based on predicate encryption. In predicate encryption, given
a master key pair, decryption keys associated with specific predicates can be
derived. Messages, and attribute sets, are encrypted with the master public key,
such that the resulting ciphertext can only be decrypted with a decryption key
associated with a predicate that is satisfied by the attributes in the
ciphertext. Assume an attribute space that can be represented by binary strings
in a set $\Sigma$. On one hand, policies defined by verifiers in \cite{dmm+18}
are encoded
as binary circuits through strings in $\Sigma$ too\footnote{\todo{This seems
    like an abuse of predicate encryption, as encryption receives a predicate,
    rather than an attribute set.}}, which can thus be associated to
ciphertexts through the predicate encryption process. On the other hand,
credentials received by users are decryption keys on a generic policy $f$, with
a hardcoded set of attributes (the attributes that the user is granted), that
can evaluate circuits. Then, intuitively, in order for a verifier to check
whether a user owns an attribute-based credential meeting certain policy $g$, it
creates a ciphertext, associating as attribute an encoding a circuit for $g$
(that belongs to $\Sigma$). If the user can decrypt this ciphertext, the
verifier accepts, as this means that the decryption key in the user's credential
has a hardcoded set of attributes that makes $g$ evaluate to true. This only
supports public attributes
(i.e., known to the issuer), though. A negative part of this approach is that
credential showings can only be interactive, whereas in the randomizable proofs
approach, they can be made non-interactive too.

\subsubsection{Main Security Models.}
%
All AC systems include \emph{anonymity} and \emph{unforgeability} as main
security properties. Up to minor variations depending on extra functionality,
anonymity typically captures that, concerning a user's credential, nothing
should be learnt by third parties that the user does not explicitly reveal.
E.g., for ACs that support multiple attributes and selectively disclosing
subsets of them, anonymity captures that the information leaked during a showing
of such credential is limited to the subset of attributes voluntarily revealed
by the user. In multi-show credentials, anonymity also captures that two
different showings must be unlinkable.
As mentioned, further variations in the functionality affect anonymity --
e.g., in systems supporting delegation, the delegation chain may be required
to be kept private.
% 
Concerning unforgeability, it basically captures that no adversary can make
a verifier accept a credential that has not been honestly produced by an
issuer of the system. Again, there are variations to this. For instance, when
credentials are composed of attributes that can further be selectively
disclosed. In this case, the adversary should not be able to prove ownership
of a set of attributes not contained within the set of attributes that have
been obtained by the adversary or leaked to it.

Special mention is worth to the model variation in \cite{hs21}, which divides
the user into two entities: core and helper, thus taking anonymous credentials
closer to DAA. This is reflected into the model by adding a property named
\emph{dependability}, which requires that no adversary should be capable to
show an honestly generated credential withouth compromising the core entity.

On the approach to formalize AC security notions, game-based definitions tend to
be more frequent \cite{bcc+09,cks10,cl11,cklm14,cmz14,ckl+15,dmm+18,fhs19,hs21},
also including definitions in the simulation paradigm. The UC framework
has also been used \cite{cdhk15}.

\subsubsection{Variations in functionality.}
%
\paragraph{Attributes, selective disclosure, and expressiveness.} %
Multi-attribute and multi-show credentials are the most frequent
\cite{cks10,cl11,cdhk15,ckl+15,fhs19,sms+19,halp20,hs21}, although one-show
credentials have also been studied \cite{bran00}.
Similarly, selective disclosure has also been more studied
\cite{cks10,cl11,cdhk15,sms+19,halp20,hs21}, when compared to 
more expressive AC systems \cite{bcc+09,cklm14,dmm+18}, while \cite{fhs19}
supports selective disclosure and restricted policies (specifically,
conjunctions), for the sake of efficiency. Probably, the higher attention to
selective disclosure so far is due to the fact that the building blocks enabling
efficient constructions with high expressiveness (such as SNARKs and functional
encryption) are recent in the cryptographic literature.

\paragraph{Security and privacy against issuers.} %
Blind issuance, i.e., letting users include in their credentials attributes that
are kept hidden from issuers, is also frequent (and certainly useful to, e.g.,
include secret keys; or support private attributes in general)
\cite{cklm14,ckl+15}, although it is also frequent to assume (even implicitly)
that the issuer \emph{needs} to learn the attributes it signs, and thus private
attributes are not considered, e.g. as in \cite{dmm+18,fhs19,sms+19}.
%
Threshold issuance is also interesting for decentralized scenarios, as it
protects against misbehaving issuers, but it was only considered recently in
\cite{sms+19} and, consequently, in \cite{halp20} (which actually builds on
\cite{sms+19}).

\paragraph{Delegation.} %
Delegation has gained attention in the last decade \cite{bcc+09,cklm14},
including delegated verification \cite{dmm+18}, as well as supporting more
expressive proofs \cite{cklm14,dmm+18}. While the latter is indeed possible in
the early works (one can use general zero-knowledge proofs on discrete
logarithms given a CL-, BBS- or PS16- based credential) it is worth noting that
the costs are probably too high. An interesting learning, that can be extracted
from \cite{cklm14}, is that we can see delegation as a sort of policy that can
be checked with expressive policies.

\paragraph{Revocation.} %
Perhaps surprisingly, revocation is not a common functionality, although it is
certainly considered by several works, e.g. \cite{cl01,cks10,ckl+15}, and for
some it is just sketched \cite{hs21}.

\paragraph{Credential aggregation.} %
And, finally, an interesting variation that only one work seems to target,
is that of efficient aggregation of credentials created by different issuers
\cite{cl11}. As in the topic of expressiveness, the conventional approach
can easily be extended to support this: e.g., if the owner of credential A and
credential B wants to use both credentials in the same showing, she just has to
prove that they share the same secret key (although this is only possible in
schemes that embed a user secret within the credential). Still, even if
possible, this process is inefficient. \cite{cl11} leverages aggregatable
signatures, which target precisely that setting.

@@

\subsubsection{Main challenges and interesting lines of work.}
%
\note{I find interesting that, given that ACs and group signatures are
  essentially the same thing, there is no work (or I have not come across it)
  trying to connect both. Specifically, the following questions:}

\begin{itemize}
\item Anonymity properties in ACs and GSs are roughly similar. However, concerning
  unforgeability-related properties:
  \begin{itemize}
  \item The notion of traceability in GSs seems incompatible in AC systems that
    do not include a user secret key in the credentials. Even for AC systems that
    do include it, unforgeability in AC is different than traceability, as there
    is no guarantee that a credential can be traced to a ``join'' process. Or
    there is?
  \item The notion of non-frameability of GSs does not seem to have an equivalent
    in ACs. I find this kind of surprising from a practical point of view, as an
    adversary in AC systems can very well aim at impersonating an honest user,
    which may then carry consequences (e.g., legal actions) for the honest user.
  \item Maybe I'm wrong in the two previous points, and we can draw a connection
    between (some basic notion of) unforgeability in ACs, and the usual notions
    of traceability and non-frameability in GSs. If I recall correctly, the
    \cite{bmw03} paper merged non-frameability and traceability into
    unforgeability, and this was later divided again in \cite{bsz05}. Check the
    reasoning again...
  \end{itemize}  
\item I find very surprising that essentially all the body of work in ACs is
  based on what seems to be the sign-randomize-proof approach of GSs, yet there
  is nothing (or I have not seen it) similar to the encrypt-then-prove approach.
  Can we do it? This may be due to the fact that revocation has not been
  considered as a main requirement in ACs (which, IMHO, is a drawback if we want
  systems applicable in the real world).
  \begin{itemize}
  \item Can we come up with a black-box construction of ACs from GSs, or vice
    versa? It should not be hard, and this may open a completely new breed of
    ACs (i.e., those based on the encrypt-then-prove approach).
  \end{itemize}
\end{itemize}

\subsection{Related Primitives and Systems}
\label{ssec:acrelated}

@@

\begin{itemize}
\item Idemix.
\item Hyperledger Indy.
\item U-Prove.
\end{itemize}

### 2021-11-26 prism-backend/research/soa_review/app-gs.tex
Polished version. Still early draft, but at least readable (excluding DAA section, which is not a priority for now).

\section{Group Signatures}
\label{sec:gs}

\paragraph{Main intuition.}
%
Group signatures were first proposed by Chaum and van Heyst in 1991 \cite{ch91}
as a privacy-respectful extension to conventional digital signatures.
The intuition is simple: in order to avoid revealing the identity of the signer,
we make her signatures look indistinguishable to the signatures of all other
members of a group. Then, any entity with access to the group public key can
verify that a group signature comes from a member of the group, but cannot
tell which specific one actually created it.
%
Beyond this, group signature schemes have one main feature: a (set of) group
manager(s) control who can become a member of the group. Also, most frequently,
a (set of) group manager(s) decide when to expell a member from the group, or
when to re-identify the creator of a specific signature.
%
The initial idea put forward in \cite{ch91} had, as is to be expected, a number
of limitations. In the following years, the seminal work was extended, both
formally, functionally and efficiency-wise.

\subsection{Approaches, Models, and Variations}
\label{ssec:gsapproach}

\subsubsection{Main approaches.}
%
There are two main ways that are recurrently used to instantiate group signature
schemes: \emph{Sign-Encrypt-Prove} and \emph{Sign-Randomize-Prove}. In both
variants, when new members of the group join, they receive a credential (i.e.,
a signature by the issuer) derived from a secret they choose. Then, when
creating a group signature, they prove control a valid credential and the
associated secret. The difference lies on how this credential is kept hidden
from the verifier.
%
In the sign-encrypt-prove variant, proposed in \cite{bmw03}, signers
encrypt their credential with a \doubt{IND-CCA2? what type?} scheme and then
create a NIZK \needcite proof of knowledge of such a valid credential
over their secret (plus the message they want to sign). This typically results
in schemes with more efficient openings, as the opening authority just has
to decrypt the encrypted credential. However, group signatures require more
space.
%
In the sign-randomize-prove variant, proposed in \needcite \todo{Get Shorty?},
credentials are actually randomizable signatures by the issuer. Signers then
randomize the signature (credential), and create a NIZK proof of knowledge that
this credential is issued for a secret they know (again, plus the message
they want to sign). This usually results in schemes with less efficient openings,
as the opening authority needs to iterate over the registered credentials until
finding the one from which the randomized credential was derived. However, the
produced group signatures are also shorter.

When a new user wants to become a group member, a common habit is also to have
her prove ownership of a conventional digital identity. This identity is then
added to the de-identifying information leveraged by the opening authority, in
order to be able to associate (anonymous) group signatures to a real-world
identity. These conventional digital identities can be any type of PKI-based
(e.g. X.509 or equivalent) certificate. \todo{This is important for
  non-frameability! Check \cite[Section 3.2]{cdl+20} and re-state this.}
\todo{This is indeed necessary for non-repudiation (mentioned in
  \cite[Section 4]{lpy12}).}
\todo{Typically used in schemes with verifiable openings. See
  \cite[Section 1.3.3]{bsi12}.}

\subsubsection{Main security models.}
%
Security for group signatures is given in the form of game-based definitions
\needcite.
The first formal security model appeared in \cite{bmw03}. It captured security
for groups with a prefixed set of members, added by the group manager upon the
creation of the group. This static requirement was too restrictive to be
realistic, and was quickly extended in \cite{bsz05} and \cite{kty04,ky06}, to
model that new users can join the group after it has been created. The models
in \cite{bsz05,kty04,ky06} are usually referred to as dynamic or partially
dynamic. \cite{bcc+16} generalizes the (partially) dynamic setting into a fully
dynamic model, which considers extra desirable security properties when users
can be revoked (i.e., removed from the group).

Up to some subtleties, the main security properties in most works that appeared
after \cite{bmw03,bsz05,kty04,ky06} are as follows:

\begin{itemize}
\item {\bf Anonymity}. This is the core property concerning privacy. It
  ensures that given a signature produced by one out of two honest (challenge)
  users picked at random from the set of honest group members, it should be
  unfeasible to determine which one actually created it.

\item {\bf Traceability}. This property (covered by the misidentification attack
  in \cite{kty04,ky06}, and spaning also non-frameability in \cite{bmw03})
  captures that it must be possible (by the proper authority) to unambiguously
  recover the identity of the signer of any valid group signature.

\item {\bf Non-frameability}. This property (considered in the framing attacks
  in \cite{kty04,ky06}) requires that no adversary should be able to create
  valid signatures that can be used to incriminate honest users by having them
  open to an honest user who did not create them.

\end{itemize}

\cite{bcc+16} also includes a trace soundness property, ensuring that signatures
can be associated (via opening proofs) to only one user \todo{why does this not
  appear in the other models? Maybe because they don't support verifiable
  openings? Check \cite{kss19} and, if so, move this to the variations in
  functionality.}

\subsubsection{Variations in functionality.}
%
Note that, while the security properties just described roughly have the same
purpose across models, there are still differences making some models stronger
or more general than others in some respects. This includes subtleties like who
generates the keys of the authorities (the environment vs the adversary), how
many queries can be made to the challenge oracles and whether or not the
signatures are fixed, etc. However, while important, there are usually generic
techniques that allow to migrate from one variant to another \todo{\needcite,
  ellaborate more, or rewrite}. Now we are interested in revisiting some of
the variations that have impact into the functionality that schemes
following each model can provide, or variations that are specific to group
signatures schemes and do not appear in other cryptosystems.

\paragraph{Separating issuer and opener.}
In some schemes \cite{bmw03,kty04} one single authority concentrates the
power to add new members to the group, and open signatures. This endows such authority with great
power -- and trust -- and is therefore one of the main concerns for privacy
advocates: not only this authority can prevent users from joining (in the case
of dynamic groups), but it can also reidentify group members. In order to reduce
this trust, and since it is a clear distinction between both functionalities
(issuing and opening), many schemes separate both roles into an issuer and an
opener. While both authorities need to be trusted for their respective tasks,
one can now make independent assumptions and even ensure certain properties
if only one of the two authorities is compromised or malicious. For instance,
non-frameability can be achieved even when both authorities are malicious;
traceability can be achieved with malicious openers; and anonymity can be
kept as long as the opener is honest. This is the case in \cite{bsz05} and
\cite{ky06} (which, although starts from a single authority, also considers
and formalises the case of separate authorities).

\paragraph{Protecting against corrupt authorities.}
Even when the issuance and opening functionalities are separated, as mentioned,
each entity can unilaterally break crucial properties in a group signature scheme.
While placing such kind of trust may be reasonable in some use cases, it may not
be so for others. Thus, a natural extension is to reduce this trust as much as
possible. In this direction, there have been works that have applied threshold
and similar techniques \needcite to require that a set of openers (as opposed
to a single opener) need to cooperate in order to open any group signature
\cite{bcly08} \needcite.
Recently, the role of the issuer was also subject to these techniques
\cite{cdl+20}, and it is now known how to produce group signatures such that no
single entity can prevent users from joining nor reidentify them.

\paragraph{Forward security.}
Forward security aims at restricting the impact of security compromises (e.g.,
key leakage) to the future: i.e., if an attacker gains control of a user's
private key, only signatures produced after the compromise should be considered
invalid. In schemes that do not ensure forward secrecy, such a compromise also
renders invalid signatures produced before the compromise. Note that, for
conventional signatures, only the compromised users is (directly) affected by
such event. However,  in group signatures, all group members are directly
affected, as the signer's identity is not revealed by the signature. Thus,
in order to learn whether or not a past signature was issued by a compromised
user, it is necessary to resort to the opener -- therefore, reidentifying
\emph{all} users in the system.
%
Forward security has been introduced in group signatures in works like
\cite{song01,ly12} \needcite.
%
Interestingly (but logically), the approach to incorporate this property
holds similarities with the functionality to implement fully dynamic group
signatures: for forward security, users are usually required to apply an
update procedure to their private keys \cite{ly12}; in fully dynamic group
signatures, it is the group manager (or the opener) who has to update some
key material \cite{bcc+16}. In both cases, time has to be discretized in epochs,
and conditions are introduced into the security properties that prevent an
adversary being able to deanonymize (produce) a valid signature generated
(using) a key in an epoch in which such key was not supposed to be active
(either because the user updated it -- in a forward secure scheme -- or the
group manager revoked it -- in a fully dynamic scheme).

\paragraph{Revocation mechanisms.}
Verifier Local Revocation \cite{bs04}, accumulators approach.

\paragraph{Opening controls.}
Even when separating the roles of the authorities or distributing them, the
fact that some entity (or set of entities) can open group signatures is still
a delicate matter that creates friction. A minimal control is to enable the
opener to prove that the opening process has been performed honestly. This is
precisely what is done by schemes that support \emph{verifiable opening}
\needcite. To further aleviate this issue, some schemes
introduce mechanisms to even prevent opening as long as some condition is
met. For instance, in \cite{seh+12,ehk+19}, the condition is determined by
the message (e.g., only signatures over offending messages can be opened).
To implement this, the authors introduce an extra authority, the
\emph{admitter}, such that the opener needs to get some information from the
admitter in order to be able to open signatures over some specific message.
In \cite{sbm10}, the authors propose \emph{contractual} anonymity: before a user
is able to anonymously access some service, both user and service sign a
contract defining the conditions upon which anonymity can be revoked. This
contract can only be enforced by a trusted entity, the \emph{accountability
  service} who runs a trusted execution environment (such as today's Intel
SGX \needcite) ensuring that the conditions are checked in a trustworthy manner.

\paragraph{Alternatives to opening.}
%
Even with separated authorities, with distributed openers, or with more generic
opening controls such as message-dependent opening, opening may not even be
the type of reduction of privacy that is necessary. In this vein, alternative
schemes have been proposed that do not include any kind of
opening at all.
%
In the schemes proposed in \cite{kty04,cpy06,bcly08}, there is an extra
authority that can produce \emph{tracing} trapdoors on a per-user basis.
Once the tracing trapdoor for a specific user is given to some entity, this
entity can link (or trace) all group signatures produced by that user.
These trapdoors are also an effective mechanism for implementing verifier-local
revocation.
%
In \cite{gl19}, the opener is replaced by a \emph{converter} who, rather than
opening any given group signature, can link sets of signatures. More
specifically, when queried with a set of signatures, the converter transforms
them so that every signature coming from the same user gets assigned a same
randomized pseudonym. Furthermore, to prevent the converter from gradually
relinking all the signatures, these conversions are non-transitive: i.e.,
signatures produced by user $A$ will receive a different randomized pseudonym in
different queries.
%
In \cite{dl21}, there is directly no trusted entity that can open or link group
signatures. Instead, every user can create proofs of several signatures having
been issued by herself. In this case, the authors also propose a scheme whereby
a user can prove sequentiality of a set of signatures: i.e., that all signatures
were produced by herself, and no signature has been omitted or inserted into the
sequence, which is also given in the order in which the original signatures were
produced.

\subsubsection{Efficiency.}

\begin{itemize}
\item Size of (group) keys.
\item Size of signatures.
\item Verification time (batching, including revocation checks...)
\item Accumulators.
\end{itemize}

\subsubsection{Main challenges.}

Efficiency is possibly good for many real-world cases. Still: utility
and unavailability of implementations.

\note{Concurrent joins -- avoid extraction \cite{ky05,klap20}.}

\subsection{Related Primitives}

\subsubsection{Ring Signatures}
\label{sssec:rs}

\cite{rst06}

\cite{bcc+15} uses ring signatures to build a fully dynamic group signature
scheme.

\subsection{Applications}
\label{ssec:gsapplication}

See \cite[Section 1.2.3]{bsi12}: it seems mostly theoretical applications.

\subsubsection{Theory}
\label{sssec:gstheoryapp}

GS-MDO imply IBE \cite{ehk+19}.
GS are implied (shouldn't his by imply?) by trapdoor permutations \cite{bmw03}.
GS imply one-way functions \cite{romp90}.
GS imply public key encryption \cite{aw04}.
Commitments from group signatures (group signatures imply commitments?)
(ref. 25 in \cite{bfg+11}).

\subsubsection{Real World Deployments}
\label{sssec:gsrwdeploy}

\cite{ehk+19} mentions anonymous auctions, anonymous bulletin boards and
anomaly detection systems.

Maybe make some comments on how to deploy gs schemes, or what aspects may be
relevant. For instnace, some schemes/models (e.g. \cite{ly12}) assume a
trusted party who generates the keys for the authorities. While this has
a big impact in security/trust model, in the real world it would probably
be circumventable with audited processes for most use cases. Also, the
issue with concurrent issuance and the approach we took for implementing
\cite{gl19} in ICT4Cart, or the limitation to logarithmic numbers of users, etc.

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "sok-privsig"
%%% End:

>>>>

\section{Log on Review of Group Signatures schemes}
\label{app:ac}

@@
